\documentclass[10pt, letterpaper]{article}

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in, top=0.35in, bottom=0.35in]{geometry}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{microtype}

% ---------- Layout ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{\small Last updated: \today}
\fancyfoot[C]{\small Juan Gabriel Vald\'{e}s D\'{i}az}
\fancyfoot[R]{\small Page 1 / 1}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---------- Section style ----------
\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{2pt}

% ---------- List style ----------
\setlist[itemize]{
    noitemsep,
    topsep=1pt,
    parsep=0pt,
    partopsep=0pt,
    leftmargin=1.5em,
    label=\textbullet
}

% ---------- Helpers ----------
\newcommand{\jobtitle}[4]{%
    \textbf{#1} \hfill \textit{#2}\\[-1pt]%
    \textit{#3} \hfill #4%
}
\newcommand{\jobstack}[1]{\vspace{0pt}\textit{\small Stack: #1}}
\newcommand{\entrysep}{\vspace{4pt}}

% ============================================================
\begin{document}
% ============================================================

% ---------- Header ----------
\begin{center}
    {\Huge\bfseries Juan Gabriel Vald\'{e}s D\'{i}az}\\[3pt]
    Montevideo, Uruguay\\[2pt]
    \href{https://linkedin.com/in/jg-valdes}{LinkedIn}
    \textbar\
    \href{https://github.com/jg-valdes}{GitHub}
    \textbar\
    jgvaldes1992@gmail.com
    \textbar\
    (+598) 96303830
\end{center}

\vspace{1pt}

% ---------- About Me ----------
\section{About Me}

Senior Backend Engineer with 8+ years building scalable REST APIs and distributed systems across
ad-tech, HR-tech, and e-commerce. Deep expertise in Python/Django; growing proficiency in
Java/SpringBoot. Proven record leading features in high-growth, fully remote SaaS products.

% ---------- Experience ----------
\section{Experience}

\jobtitle{Senior Backend Engineer}{Uruguay (Remote)}{SunnyData AI}{Aug 2025 -- Present}
\begin{itemize}
    \item Develop FastAPI and SpringBoot services for Kroger's 8451 Ad Platform, enabling campaign
          and ads management across all Kroger retail sites.
    \item Configured Azure secrets, GitHub Actions, and Terraform pipelines for CI/CD; authored
          Postman contract tests to enforce API contracts across services.
\end{itemize}
\jobstack{Python 3.8+, FastAPI, Java, SpringBoot, Kubernetes, Azure, Redis, MongoDB}

\entrysep

\jobtitle{Senior Software Engineer}{Uruguay (Remote)}{UKG -- Employee Voice}{Jan 2023 -- Jul 2025}
\begin{itemize}
    \item Led REST API development for UKG Pro's Employee Voice survey tool, building automation
          rules for survey triggering, participant generation, and multi-channel invite delivery.
    \item Re-architected Celery Beat pipelines for survey tracking and aggregation, improving
          processing throughput.
    \item Designed a Java 21 + SpringBoot service layer to migrate the legacy Employee Voice
          platform to a centralized, standards-compliant data service.
\end{itemize}
\jobstack{Python 3.8+, Java, SpringBoot, AngularJS, Redis, MySQL, MongoDB, Celery, Kubernetes, GCS}

\entrysep

\jobtitle{Backend Developer}{Cuba (Remote) $\to$ Spain}{Smart and Fun -- PlusHolidays}{Nov 2019 -- Sep 2022}
\begin{itemize}
    \item Built REST API services for a Spanish holiday reservation platform, delivering full-CRUD
          modules for Accommodations, Notifications, and Settings.
    \item Integrated Inter Home Group and Avantio VRMS for real-time booking and accommodation
          synchronization; implemented Celery tasks and WebSocket notifications for async events.
\end{itemize}
\jobstack{Django 3, DRF, Python3, PostgreSQL+PostGIS, Redis, Celery}

\entrysep

\jobtitle{Full-Stack Developer}{Cuba (Remote) $\to$ USA}{Locomotion Technologies -- WHATISHOT}{Jan 2017 -- Aug 2022}
\begin{itemize}
    \item Built an async search module via Django-RQ capturing user behavior data across filter
          forms, and integrated Google Merchant Center to generate Google Shopping product feeds.
    \item Implemented SendGrid webhook handlers, Meta SEO for product pages, and wrote unit tests
          covering models, forms, serializers, views, and utilities.
\end{itemize}
\jobstack{Django 2.2, DRF, Python3, Docker, AWS S3, PostgreSQL+PostGIS, Redis, JavaScript, jQuery}

% ---------- Skills ----------
\section{Skills}

\begin{itemize}
    \item \textbf{Languages \& Frameworks:} Python3, Django, DRF, FastAPI, Java, SpringBoot, Celery, JavaScript, jQuery
    \item \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis
    \item \textbf{Infrastructure:} Docker, Kubernetes, Azure, GCS, AWS S3
    \item \textbf{Methods:} REST API Design, Scrum, Git
\end{itemize}

% ---------- Education ----------
\section{Education}

\jobtitle{Universidad de las Ciencias Inform\'{a}ticas}{La Habana, Cuba}{Computer Science Engineer}{2011 -- 2016}

% ---------- Certifications ----------
\section{Certifications}

\begin{itemize}
    \item \textbf{PCAP\texttrademark{} -- Certified Associate Python Programmer} \hfill Mar 2024\\
          \textit{OpenEDG / Python Institute}
    \item \textbf{Scrum Fundamentals Certified} \hfill Jul 2021\\
          \textit{SCRUMstudy}
\end{itemize}

\end{document}
